### 2016-08-23 results.tex
cheers

\heading{Correctness. }  Here we give security proofs and attacks with respect to the correctness notions.
\begin{itemize}
\item Show Bloom Filter is correct in the ROM %\jnote{Would be good to show that RO-based Bloom filter is FP-secure.}
\item correctness security/attacks on bigram/PRF-based double-hashing construction ($h_j(x) = F_{K1}(x) + j\cdot F_{K2}(x) \bmod m$ where the~$x$ are bigrams of names, etc.) 
\item correctness-security/attacks on bigram/domain-separated PRF construction ($h_j(x)=F_K(\langle j,x \rangle) \bmod m$, or just assume range of~$F$ is $[m]$.)
\item correctness-security/attacks Dong, Chen, Wen ``garbled Bloom filter'' construction
\item ...
\end{itemize}

@@

\item Prove a privacy bound for the bigram/PRF-based double-hashing construction that Neidermayer et al.\ attacks. I'm pretty sure the attack is in the public-BB setting, and the provable security bound is considerably worse than the min-entropy because of the way the representation is made.  (Essentially, the Hamming weight of the representation is a good estimate of the length of the longest surname in filter.)

\item Attack privacy of Dong, Chen, Wen ``garbled Bloom Filter'' construction in the BB-hash setting \tsnote{I give the attack in the related work section.  Copy it here and flesh it out.}  Prove privacy of construction in secret-hash setting.  \tsnote{Makes the point that the application setting really matters.}

@@

\item Show implications and/or separations between FP and privacy notions. \tsnote{Belongs in previous section.}

\item \tsnote{...}
\end{itemize}

>>>>

\heading{Correctness. }  Here we give security proofs and attacks with respect to the correctness notions.
\begin{itemize}
\item Show Bloom Filter is correct in the ROM 
\item correctness security/attacks on bigram/PRF-based double-hashing construction ($h_j(x) = F_{K1}(x) + j\cdot F_{K2}(x) \bmod m$ where the~$x$ are bigrams of names, etc.) 
\item correctness-security/attacks on bigram/domain-separated PRF construction ($h_j(x)=F_K(\langle j,x \rangle) \bmod m$, or just assume range of~$F$ is $[m]$.)
\item correctness-security/attacks Dong, Chen, Wen ``garbled Bloom filter'' construction

\end{itemize}

@@

\item Prove a privacy bound for the bigram/PRF-based double-hashing construction that Neidermayer et al.\ attacks. I expect that the provable security bound is considerably worse than the min-entropy because of the way the representation is made.  (Essentially, the Hamming weight of the representation is a good estimate of the length of the longest surname in filter.)

\item Attack priv-security of Dong, Chen, Wen ``garbled Bloom Filter'' construction when the hash functions are public.\tsnote{I give the attack in the related work section.  Copy it here and flesh it out.}  Prove priv-security privacy of construction when hash functions are secret.  \tsnote{Makes the point that the application setting really matters.}

@@

\item ...
\end{itemize}
